Scalar on Function Regression \\ with Applications to Near-Infrared Spectography

### 2022-01-07 Presentation/slides.tex
Increment

% packages
%\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{setspace}
%\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[font=small,skip=2pt]{caption}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

	\begin{frame}{Plots}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
				\includegraphics[width=\textwidth]{../Graphics/Growth_curves.png}
				\caption{\tiny Growth curves of 54 girls age 1-18}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
				\centering
				\includegraphics[width=\textwidth]{../Graphics/NIR.png}
				\caption {\tiny NIR spectrum of 60 gasoline samples}
			\end{minipage}
		\end{figure}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If a function $f(t)$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called \textbf{Square Integrable Function}\\
		and in the set $\mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

@@

	%\begin{frame}{Theory}
	%	Jakob
	%	\begin{itemize}
	%		\item Random function represented as linear combination of basis functions $\checkmark$
	%		\item Just transform to multiple linear regression setting $\checkmark$
	%		\item You already know that from the beginning $\checkmark$
	%	\end{itemize}
	%\end{frame}

@@

		\begin{itemize}
			\item This allows us to write each observation in the data set as $\{y_i, Z_{i,1}, Z_{i,2}, \dots\}$
			\item Truncating the functional basis yields an approximation $\{y_i, Z_{i,1}, Z_{i,2}, \dots, Z_{i,L}\}$
		\end{itemize}

@@

	%\begin{frame}{Theory - FPCA}
	%	Jakob
	%	\begin{itemize}
	%		\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
	%		\item Introduce mean and covariance functions of random functions $\checkmark$
	%		\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
	%		\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
	%		\item Plot fpcs and approximation of function realization
	%	\end{itemize}
	%\end{frame}

	%\begin{frame}{Spectral Representation of Random Vectors}
	%	Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.

	%	\begin{itemize}
	%		\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
	%		\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
	%		\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
	%	\end{itemize}

	%	\vspace{0.2cm}
	%	Then $X$ can also be represented as
	%	$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
	%	where the $\xi_i(\omega)$ have the following properties

	%	\begin{multicols}{2}
	%		\begin{enumerate}
	%			\item $\mathbb{E}[\xi_i(\omega)] = 0$
	%			\item $Var(\xi_i(\omega)) = \lambda_i$
	%			\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
	%		\end{enumerate}
	%	\end{multicols}
	%\end{frame}

@@

	%\begin{frame}{Principal Component Analysis}
	%	A related concept is \textbf{Principal Component Analysis} (PCA).
	%	\vspace{0.2cm}
	%	
	%	$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
	%
	%	\begin{itemize}
	%		\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
	%		\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
	%		\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
	%		\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
	%	\end{itemize}
	%	\vspace{0.2cm}

	%	Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
	%	\begin{multicols}{2}
	%		\begin{enumerate}
	%			\item $\mathbb{E}[Z_i(\omega)] = 0$
	%			\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
	%			\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
	%		\end{enumerate}
	%	\end{multicols}
	%\end{frame}

	\begin{frame}{Functional Principal Component Analysis}
		{\color{red} Rephrase this!} This idea can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
		\vspace{0.2cm}

@@

	\begin{frame}{Simulation Setup \& Application cont.}
		%\begin{itemize}
		%\item
		Following \textbf{Reiss and Ogden (2007)}, let $f_1(t)$ and $f_2(t)$ be two coefficient functions: 
		%\vspace{0.2cm}

   		%$f_1(t) = 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t)$\\
   		%\vspace{0.1cm}

        %$f_2(t) = 1.5 \exp(\frac{-0.5(t-0.3)^2}{0.02^2}) - 4 \exp(\frac{-0.5(t-0.45)^2}{0.015^2}) +  8 \exp(\frac{-0.5(t-0.6)^2}{0.02^2}) - \exp(\frac{-0.5(t-0.8)^2}{0.03^2})$

		%\end{itemize}
		\vspace{0.1cm}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
  				\includegraphics[width=\textwidth]{smooth_function.png}
  				\caption{$f_1(t)$, smooth function}
  				\label{fig:test1}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
	  			\centering
  				\includegraphics[width=\textwidth]{bumpy_function.png}
  				\caption{$f_2(t)$, bumpy function}
  				\label{fig:test2}
			\end{minipage}
		\end{figure}

@@

	\begin{frame}{further reading}
		Put footnotes here!
	\end{frame}

>>>>

% packages
%\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage{setspace}
%\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[font=small,skip=2pt]{caption}
\captionsetup[figure]{labelformat=empty}
\usepackage[
backend=biber,
style=authoryear-comp,
]{biblatex}

@@

	\begin{frame}{Plots}
		\begin{minipage}{.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{../Graphics/Growth_curves.png}
				\caption{Growth curves of \\ 54 girls age 1-18}
			\end{figure}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\begin{figure}
				\includegraphics[width=\textwidth]{../Graphics/NIR.png}
				\caption{NIR spectrum of 60 \\ gasoline samples}
			\end{figure}
		\end{minipage}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If a function $f(t)$ satisfies
		$$\int_{0}^{1} \left(f(t)\right)^{2}dt < \infty$$
		the function $f(t)$ is called \textbf{Square Integrable Function} written $f(t) \in \mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

@@

@@

		\begin{itemize}
			\item This allows us to write each observation in the data set as $\left(y_i, Z_{i,1}, Z_{i,2}, \dots \right)$
			\item Truncating the functional basis yields an approximation $\left(y_i, Z_{i,1}, Z_{i,2}, \dots, Z_{i,L}\right)$
		\end{itemize}

@@

@@

	\begin{frame}{Functional Principal Component Analysis}
		\textbf{Principal Component Analysis} can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
		\vspace{0.4cm}

@@

	\begin{frame}{Simulation Setup \& Application cont.}

		Following \textbf{Reiss and Ogden (2007)}, let $f_1(t)$ and $f_2(t)$ be two coefficient functions:

		\vspace{0.1cm}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
  				\includegraphics[width=\textwidth]{smooth_function.png}
  				\caption{$f_1(t)$, smooth function}
  				\label{fig:test1}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
	  			\centering
  				\includegraphics[width=\textwidth]{bumpy_function.png}
  				\caption{$f_2(t)$, bumpy function}
  				\label{fig:test2}
			\end{minipage}
		\end{figure}

@@

	\begin{frame}
		\topskip0pt
		\vspace*{\fill}
		\begin{center}
			{\LARGE Thank you for your time!}
		\end{center}	
		\vspace*{\fill}
		%
	\end{frame}

	\begin{frame}{Further Reading}
		 Put footnotes here!
	\end{frame}

	% From here on out are the supplementary slides.

	\begin{frame}{Spectral Representation of Random Vectors}
		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.

		\begin{itemize}
			\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
			\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
			\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
		\end{itemize}

		\vspace{0.2cm}
		Then $X$ can also be represented as
		$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
		where the $\xi_i(\omega)$ have the following properties

		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $Var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

	\begin{frame}{Principal Component Analysis}
		A related concept is \textbf{Principal Component Analysis} (PCA).
		\vspace{0.2cm}

		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}

		\begin{itemize}
			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
		\end{itemize}
		\vspace{0.2cm}

		Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[Z_i(\omega)] = 0$
				\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
				\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}
